% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%       release v3.0, 16th July 2014
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997, 2014 Cambridge University Press

\documentclass{jfm}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\shorttitle{Generalized Hydraulic Theory}
\shortauthor{Henri F. Drake, and L. Pratt}

\title{Hydraulic control of rotating, stratified flow with non-zero potential vorticity}

\author{Henri F. Drake\aff{1,2}
  \corresp{\email{henrifdrake@gmail.com}} \and
  L. Pratt\aff{2}}

\affiliation{\aff{1}Department of Earth, Atmospheric, and Planetary Sciences, Massachusetts Institute of Technology,
Cambridge, MA 02139, USA
\aff{2}Woods Hole Oceanographic Institution, Woods Hole, MA 02139, USA}

\begin{document}

\maketitle

\begin{abstract}
Abstract coming soon. 
\end{abstract}

\begin{keywords}
\end{keywords}

\section{Introduction}

The deep ocean is largely fed by a handful of localized overflows. At these overflow locations, newly formed dense waters in shallow seas flow through a narrow channel and spill over a sill into a deep ocean basin, mixing with- and entraining- lighter waters along their way. Similarly, the inter-basin exchanges between vast ocean basins often occur in narrow abyssal channels. The disproportionately large impact of these small-scale channels on ocean circulation and watermass properties make them ideal targets for in-situ measurement, theory, and parameterization.

Many of these overflows are thought to be hydraulically controlled, ...

\section{Background: maximal transport hydraulic control theory}

\cite{Borenas1986} and \cite{borenas_deep-water_1988} analytical solution.

\section{Stationary perturbation hydraulic control theory}

\subsection{Exact solutions in limits of zero PV, no rotation, or flat bottom}

See Larry's notes.

\subsection{Asymptotic integral solution in limit of weak rotation}

See Larry's notes.

\subsection{Numerical solution of general case}

See Henri's notes.

\section{Application of theory to nonlinear flow solutions}

TBD

\section{Discussion}

\section{Conclusions}

\bibliographystyle{jfm}
% Note the spaces between the initials
\bibliography{references}

\end{document}
